---
title: "Decision_Trees_Exercise"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tree)
library(tidyverse)
titanic <- read.csv("../week3/titanic_train.csv")
titanic_test <- read.csv("titanic_test.csv")
```

## Question 2
What percentage of passengers in our data set survived?
```{r question 2}
titanic %>% group_by(Survived) %>% summarize("count" = n()) %>% mutate(percent = count/ sum(count) * 100)
```

##Question 3
Which variables do you think may be good predictors of the survival on the Titanic?
```{r question 3}
model <- glm(Survived ~ as.factor(Pclass) + as.factor(Sex) * Age, data = titanic, family = "binomial")
summary(model)
```

##Question 4
Estimate a decision tree predicting survival using age and sex as predictors. Describe your results.
```{r question 4}
tree1 <- tree(as.factor(Survived) ~ as.factor(Sex)+ Age, titanic)
summary(tree1)
plot(tree1)
text(tree1, pretty = 0)
```

##Question 5
Estimate a decision tree using age, sex and passenger class. Describe your results.
```{r question 5}
tree2 <- tree(as.factor(Survived) ~ as.factor(Sex)+Age + as.factor(Pclass), titanic)
summary(tree2)
plot(tree2)
text(tree2, pretty = 0)
summary(tree2)
```

##Question 6
Estimate your own decision tree with your own set of predictors.
```{r question 6}
tree3 <- tree(as.factor(Survived) ~ as.factor(Sex) + Age + SibSp + as.factor(Pclass), titanic)
summary(tree3)
plot(tree3)
text(tree3, pretty = 0)
```

##Question 7
Make predictions based on test data
```{r question 7}
titanic_test$y_hat <- predict(tree3, titanic_test, type = "class")
```
