---
title: "Trip_time"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
load('../week1/trips.RData')
```
Create a function that computes historical trip times between any two stations:
Take the trips dataframe and two station names as inputs
Return a 168-by-6 dataframe with summary statistics of trip times for each hour of the week (e.g., Monday 9am, Monday 10am, etc.), where the summary statistics include:
* Average number of trips in that hour
* Average and median trip times for that hour
* Standard deviation in trip time for that hour
* Upper and lower quartiles of trip time for that hour
```{r}
trip_time <- function(df, start, end){
  hour_stats <- df %>% filter(start_station_name == start & end_station_name==end) %>% mutate(day = wday(as.Date(starttime), label = TRUE), hour = hour(starttime)) %>% group_by(day, hour) %>% 
    summarize("count" = n(), 
              "avg" = mean(tripduration/60), 
              "median" = median(tripduration/60),
              "sd" = sd(tripduration/60),
              "lower_quart" = quantile(tripduration/60, probs = .25),
              "upper_quart" = quantile(tripduration/60, probs = .75)) 
}
```

Make a plot of the results, where each facet is a day of the week, the x axis shows hour of the day, and the y axis shows average trip time, with transparent ribbons to show the standard deviation in trip time around the mean
```{r}
penn_to_grand = trip_time(trips, "8 Ave & W 31 St", "E 43 St & Vanderbilt Ave")
ggplot(penn_to_grand, aes(x = hour, y = avg)) +
  geom_point()+
  geom_ribbon(aes(ymin = avg - sd, ymax = avg + sd), alpha = .2) +
  scale_y_continuous() +
  facet_wrap(~day, scale = "free")
```